---
title: "Coverage Statistics"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This report (generated by R) shows plots and statistics exploring the relationship between nucleotide content in the reference genome to coverage.

```{r}
# Load required package and read in data generated from earlier in the pipline
require(ggplot2)
baseCov = read.csv('base_anova.csv')
gc.vs.cov = read.csv('GC_vs_cov.csv')
```


This is a box plot showing coverage distribution for each base (C,T,G,A)
```{r pressure, echo=FALSE}
covByBaseType <- ggplot(baseCov, aes(Base, Coverage))
covByBaseType + geom_boxplot() + ggtitle("Coverage by base type") + labs(x = "Base", y = "Count")
```


Below, an ANOVA test is performed comparing coverage of each base type.
```{r}
baseAnova = aov(Coverage ~ Base, data = baseCov)
summary(baseAnova)
```


Post-hoc pairwise comparison analysis
```{r}
TukeyHSD(baseAnova)
```


Plot showing how average coverage changes with average GC content. To creat this, the reference genome was split into 20bp segments and the percent GC and average coverage was taken for each segment.
```{r}
covByBaseType <- ggplot(gc.vs.cov, aes(avg.GC, avg.cov))
covByBaseType + geom_point() + ggtitle("Coverage by GC content") + labs(x = "GC%", y = "Count")
```



